\plaintitle

### 2016-05-17 cscw/papers/2017/labor/trackingWork.tex
incidental updates

Routenization can be seen in the contemporary in workflows
[\textit{There are various papers that talk about creating a workflow;
maybe this is where FFV belongs? Foundry?}].

>>>>

Routenization can be seen in the contemporary in workflows
\cite{foundry,bernstein2015soylent}
[\textit{There are various papers that talk about creating a workflow;
maybe this is where FFV belongs? Foundry?}].
